### 2024-01-08 imag.tex
New version for imag

\section{Environmental and societal impact}

\subsection{Personnal environmental impact}

@@

\subsection{Global impact}

@@

\subsubsection{Environmental impact}\label{subsubsec:envImp}

@@

The potential chip that would be created has been analyzed, there are also other aspects to take into account. The system being a way to run a wide variety of \acp{NN}, depending on the scale of the project the cip is used in, the impact of training is different. However, the main application being for embedded systems, training the system for a few hours is negligible when the final circuit is used thousands to millions times in its life cycle.
The inference of the \ac{NN} also has an environmental impact due to the power it uses. But the goal of building an analog \ac{NN} is to reduce both execution time and energy consumption, and while the energy comsumption wasn't evaluated in this thesis, it can be assumed, from the usual trend of analog circuits, a much lower energy consumption than with digital chips. This, scaled with thousands of units, offers a subtantial gain in overall power consumption.

@@

\subsubsection{Societal impact}

@@

\subsection{Host structure's policy}

The lab that hosted me during my master thesis doesn't have a policy concerning the envirnoment. \ac{INESC}-MN being a micro and nanofabrication lab, they own and run most of the machines required to fabricate chips. The machines are not state of the art and mostly used for prototyping, for the lab itself or for contracted companies. As explained in \cref{subsubsec:envImp}, those machines are very power hungry and thus explains why any other measures would be rendered useless next to this.

>>>>

\fancychapter{Environmental and societal impact}\label{cap:rse}

\section{Personnal environmental impact}

@@

\section{Global impact}

@@

\subsection{Environmental impact}\label{subsec:envImp}

@@

The potential chip that would be created has been analyzed, there are also other aspects to take into account. The system being a way to run a wide variety of \acp{NN}, depending on the scale of the project the chip is used in, the impact of training is different. However, the main application being for embedded systems, training the system for a few hours is negligible when the final circuit is used thousands to millions times in its life cycle.
The inference of the \ac{NN} also has an environmental impact due to the power it uses. But the goal of building an analog \ac{NN} is to reduce both execution time and energy consumption, and while the energy comsumption wasn't evaluated in this thesis, it can be assumed, from the usual trend of analog circuits, a much lower energy consumption than with digital chips. This, scaled with thousands of units, offers a subtantial gain in overall power consumption.

@@

\subsection{Societal impact}

@@

\section{Host structure's policy}

The lab that hosted me during my master thesis doesn't have a policy concerning the envirnoment. \acs{INESC}-MN being a micro and nanofabrication lab, they own and run most of the machines required to fabricate chips. The machines are not state of the art and mostly used for prototyping, for the lab itself or for contracted companies. As explained in \cref{subsec:envImp}, those machines are very power hungry and thus explains why any other measures would be rendered useless next to this.
